The value of intermediation

### 2022-11-17 src/presentation/micro_seminar_talk.qmd
Highlight differences compared to Anderson-Bedre

 - Axiomatic reasoning
    - The Shapley-value is the only sharing rule that is efficient, symmetric, linear, and satisfies the null player axiom [@shapley1953additive]
 - Bargaining foundations
    - The value arises of the subgame-perfect equilibrium of various alternating-offer bargaining games [e.g. @gul1989bargaining; @winter1994demand; @hart1996bargaining; @stole1996intra; @inderst2003bargaining]
 - A tractable and sensible-looking gain-sharing rule
    - Comparative statics show that it behaves as one would expect

@@

# Extensions

@@

::: {.notes}
 - Intentionally simple model
 - Most elements borrowed from [@anderson2021hybrid]
:::

## Timing of the game

 - Proposed a very tractable way of modeling bargaining applicable to certain important contexts
 - The results are for upstream-downstream situations, platform settings, and two-sided markets
 - The outcomes generally concur with intuitive expectations
 - Even the simple example application provides some interesting insights into hybrid platforms

::: {.notes}
My contributions
 - Shapley-value is a good fit for platform settings
 - The continuous case is vary tractable in this specific setting
 - Results about the weighted value are mine
 - Insight that hybrid platforms have higher bargaining power, leading to more distortion
:::

## Future work

- There is a variety of ways in which the model could be extended (e.g. additional platforms provide some value)
- The example application could be turned into a proper, full-fledged model
- A lab experiment about the outcomes of group bargaining could be conducted
- The model could be applied to other contexts

::: {.notes}
 - Some extensions are straightforward
 - However, some situations just don't fit the model
 - Essentially a plug-and-play approach when one some middle ground between one side taking all the gains
:::

# Thank you {.unnumbered .unlisted}

>>>>

 - Axiomatic reasoning
    - The Shapley-value is the only sharing rule that satisfies a nice set of axioms (efficiency, symmetry, linearity, dummy player axiom) [@shapley1953additive]
 - Bargaining foundations
    - The value arises as the subgame-perfect equilibrium of various alternating-offer bargaining games [e.g. @gul1989bargaining; @winter1994demand; @hart1996bargaining; @stole1996intra; @inderst2003bargaining]
 - A tractable and sensible-looking gain-sharing rule
    - Comparative statics show that it behaves as one would expect

@@

## The model

 - Intentionally simple model
 - Most elements borrowed from [@anderson2021hybrid]
 - Main changes:

## Hybrid platforms with lump-sum fees

::: {.column width="45%"}
::: {.fragment .fade-in fragment-index=2}
 1. Platforms set lump-sum fee $F$
:::
::: {.fragment .fade-in fragment-index=3}
 2. Firms decide whether to enter at cost $c + F$
:::
::: {.fragment .fade-in fragment-index=4}
 3. Firms and platform set product prices, consumers buy products
:::
:::

::: {.fragment fragment-index=1}
<video data-autoplay src="../../out/manim_figures/videos/market_structure_benchmark/800p60/sections/draw_objects.mp4" />
:::
::: {.fragment fragment-index=3}
<video data-autoplay src="../../out/manim_figures/videos/market_structure_benchmark/800p60/sections/platform_entry.mp4" />
:::
::: {.fragment fragment-index=4}
<video data-autoplay src="../../out/manim_figures/videos/market_structure_benchmark/800p60/sections/pricing_game.mp4" />
:::

## Outcomes

 - Constant additive markup $\implies$ profit $\propto$ market share
 - Per unit fringe profit
     $$ \frac{\mu B}{N_P B + N_F B + 1} \quad \text{where } B = \frac{v - c - \mu}{\mu} $$
 - Free entry
     $$ N_F^* = \frac{\mu B}{F + c} - N_P - \frac{1}{B} $$

## Outcomes - the platform's decision

 - Platform's profit: own sales plus entry fees
     $$ \pi_P = F N_F^* + \frac{\mu N_P B}{N_P B + N_F^* B + 1} $$
 - In a pure marketplace the second term is zero
 - Here, second term is increasing in $N_P$
 - $\implies$ higher fee and lower entry in the hybrid case

## Model with bargaining

Contributions

 - A tractable way of modeling bargaining applicable to important contexts
 - Interesting insights into hybrid platforms

Future work

- The example application could be turned into a proper, full-fledged model
- A lab experiment about the outcomes of group bargaining

::: {.notes}
My contributions
 - Shapley-value is a good fit for platform settings
 - The continuous case is vary tractable in this specific setting
 - Results about the weighted value are mine
 - Insight that hybrid platforms have higher bargaining power, leading to more distortion
 - Some extensions are straightforward, but some situations just don't fit the model
 - Essentially a plug-and-play approach when one some middle ground between one side taking all the gains
:::

# Appendix

@@
